An Invariant Framework for Conducting Reproducible Computational Science

### 2015-03-20 evaluation.tex
Remove unused stuff
Modification (according to dthain's suggestions)

\begin{table}
\small
    \centering
    \begin{tabular}{lcccc}
    \hline
    \bf Application & \bf Tool Type & \bf Obtain Namelist & \bf Create Package & \bf Re-Execution \\ \hline
	Athena & Parrot & 10 min 14 sec & 53 sec & 9 min 14 sec \\ \hline
	Athena & PTU & --- & 8min 48 sec & 7 min 21 sec \\ \hline
	TauRoast & Parrot & 22 min 50 sec  & 4 min 25 sec & 10 min 24 sec \\ \hline
	TauRoast & PTU & --- & 23 min 30 sec & 8 min 40 sec \\ \hline 
    \end{tabular}
    \normalsize
    \caption{Time Comparison between Parrot and PTU}
    \label{table:parrot_ptu}
\end{table}

@@

\begin{table}
\small
	\centering
	    \begin{tabular}{lcrr}
	        \hline
	        \bf Dependency Name & \bf Location & \bf Total Size &  \bf Used Size\\ 
	        \hline
	        CMSSW code     & CVS & 88.1GB &  5.2MB\\ \hline
	        Tau source       & Git & 73.7MB & 212KB \\ \hline
	        PyYAML binaries    & HTTP & 52MB& 0KB \\ \hline
	        .h file       & HTTP& 41KB & 0KB \\ \hline 
	        Ntuples data    & HDFS& 11.6TB & 18GB \\ \hline
	        Configuration & CVMFS & 7.4GB & 105MB \\ \hline
	        Linux commands & localFS & 110GB & 110MB \\ \hline     
	        HOME dir& AFS &12GB & 24MB\\ \hline
	        Misc commands & PanFS & 155TB & 8KB \\ \hline
	        Total      &    & 166.8TB     &  18GB \\ \hline
	    \end{tabular}
	    \normalsize
	    \caption{Data and Code Size Used by TauRoast}
	    \label{table:size-original-real}
\end{table}
%	\begin{tablenotes}
%	      \small
%	      \item The first column illustrates the total size of each data and software source; 
%	            the second column illustrates the size of the named files from each source;
%	            the third column illustrates the size of actually used data from each source.
%	            N/A denotes it is hard to figure out the named size of implicit dependencies directly.        
%	    \end{tablenotes}

@@

In Athena, the input file is 224MB and output files are 16MB. PTU build a 855MB package, while Parrot builds an 825MB package. The overhead is of provenance which is 7MB and 
some differences is dependency information.

>>>>

\begin{table}
\small
    \centering
    \begin{tabular}{lcccr}
    \hline
    \bf Application & \bf Packaging Tool & \bf Obtain Namelist & \bf Create Package & \bf Re-Run (Tool/Time)\\ \hline
	Athena & Parrot & 10 min 14 sec & 00 min 53 sec & Parrot / 09 min 14 sec  \\ \hline
	Athena & PTU & --- & 08 min 48 sec & PTU / 07 min 21 sec  \\ \hline
	TauRoast & Parrot & 22 min 50 sec  & 04 min 25 sec &chroot / 10 min 24 sec \\ \hline
	TauRoast & PTU & --- & 23 min 30 sec & PTU / 08 min 40 sec \\ \hline 
    \end{tabular}
    \normalsize
    \caption{Time Comparison between Parrot and PTU}
    \label{table:parrot_ptu}
\end{table}

@@

\begin{table}
\small
	\centering
	    \begin{tabular}{lcrr}
	        \hline
	        \bf Dependency Name & \bf Location & \bf Total Size &  \bf Used Size\\ 
	        \hline
	        CMSSW code     & CVS & 88.1GB &  5.2MB\\ \hline
	        Tau source       & Git & 73.7MB & 212KB \\ \hline
	        PyYAML binaries    & HTTP & 52MB& 0KB \\ \hline
	        .h file       & HTTP& 41KB & 0KB \\ \hline 
	        Ntuples data    & HDFS& 11.6TB & 18GB \\ \hline
	        Configuration & CVMFS & 7.4GB & 105MB \\ \hline
	        Linux commands & localFS & 110GB & 110MB \\ \hline     
	        HOME dir& AFS &12GB & 24MB\\ \hline
	        Misc commands & PanFS & 155TB & 8KB \\ \hline
	        Total      &    & 166.8TB     &  18GB \\ \hline
	    \end{tabular}
	    \normalsize
	    \caption{Data and Code Size Used by TauRoast}
	    \label{table:size-original-real}
\end{table}

@@

In Athena, the input file is 224MB and output files are 16MB. PTU builds a 855MB package, while Parrot builds an 825MB package. The overhead is of provenance which is 7MB and 
some differences is dependency information.

### 2015-03-20 intro.tex
Modification (according to dthain's suggestions)

Reproducibility is a cornerstone of the scientific method~\cite{borgman2012data}. 
Its importance is underscored by its ability to advance science---reproducing by verifying and validating a scientific result leads to improved understanding, thus increasing possibilities of reusing or extending the result. 
Ensuring reproducibility of a scientific result, however, often entails detailed documentation and specification of the involved scientific method. Historically, this has been achieved through text and proofs in a publication. 
As computation pervades the sciences and transforms the scientific method, mere text is considered insufficient. 
In particular, apart from textual descriptions describing the result, a reproducible result must also include several computational artifacts, such as software, data,  environment variables, and state of computation that are involved in the adopted scientific method \cite{Sole}.

Virtualization has emerged as a promising approach for reproducing computational scientific results. One approach is to conduct the entire computation relating to a scientific result within a virtual machine image, and then share the resulting image. This way VMIs become an authoritative, encapsulated, and executable records of computations, especially computations whose results are destined for publication and/or re-use, and the VMIs can be shared easily \cite{Lampoudi}. 
With this approach, oftentimes, the resulting image is too big in size for share-ability purposes. An alternative light-weight form of virtualization allows encapsulation of the application software, along with all its necessary dependencies into a self-contained package, but does not make it executable.
The encapsulation of the self-contained package is achieved by interposing application system calls, and only copying the necessary dependencies (data, libraries, code, etc.) into the package, which also makes it lighter weight than a VMI. While both forms of virtualization provide mechanisms for sandboxing the computations associated with a scientific result, neither form of virtualization provides any guarantee that the included pieces of software will indeed reproduce the associated scientific result.

Since reproducibility is significantly about comprehensive documentation, virtualization approaches in their current form only make it easy to capture the computations. Preserving the computations, so that they are easy to understand, install, or alter implicit dependencies that are part of computation, especially as dependencies and software components evolve or become deprecated, is not effectively addressed. There are two approaches to address the preservation challenge. By either introducing tools that help document dependencies and provide software attribution within VMIs or packages, or alternatively by using software delivery mechanisms, such as, centralized package management, Linux containers, and the, more recent, Docker framework. We examined the first approach previously in \cite{SoftProv}. 
In this paper we examine the second approach. 
In particular, we consider the light-weight virtualization approaches, because, we believe that the combination of light-weight approaches with more standardized software delivery mechanisms can lead to addressing the reproducibility challenge for a wide variety of scientific researchers. 
A package created by those light-weight approaches encapsulates all the necessary dependencies of an application, and can be used to repeat the application through different sandbox mechanisms, including Parrot, CDE, PTU, chroot, and Docker.

To conduct a thorough examination, we consider real-world complex high energy physics (HEP) applications, independently developed by two HEP groups, that must be reproduced so that the entire high energy physics community can benefit from the analysis obtained from the application. We describe challenges in reproducing the applications, and consider the extent to which reproducibility requirements can be satisfied with light-weight virtualization approaches and software delivery mechanisms. We propose an invariant framework for computational reproducibility that combines light-weight virtualization with software delivery mechanisms for efficiently capturing, invariantly preserving and practically deploying applications.
We measure the performance overhead of  light-weight virtualization and software delivery approaches.

@@

>>>>

Reproducibility is a cornerstone of the scientific method~\cite{borgman2012data}. 
Its importance is underscored by its ability to advance science---reproducing by verifying and validating a scientific result leads to improved understanding, thus increasing possibilities of reusing or extending the result. 
Ensuring reproducibility of a scientific result, however, often entails detailed documentation and specification of the involved scientific method. Historically, this has been achieved through text and proofs in a publication. 
As computation pervades the sciences and transforms the scientific method, mere text is no longer sufficient. 
In particular, apart from textual descriptions describing the result, a reproducible result must also include several computational artifacts, such as software, data,  environment variables, and state of computation that are involved in the adopted scientific method \cite{Sole}.

Virtualization has emerged as a promising approach for reproducing computational scientific results. One approach is to conduct the entire computation relating to a scientific result within a virtual machine image, and then share the resulting image. This way VMIs become an authoritative, encapsulated, and executable records of computations, especially computations whose results are destined for publication and/or re-use, and the VMIs can be shared easily \cite{Lampoudi}. 
However, the resulting image may be too big to distribute. An alternative light-weight form of virtualization allows encapsulation of the application software, along with all its necessary dependencies into a self-contained package, but does not make it executable.
The encapsulation of the self-contained package is achieved by interposing application system calls, and copying the necessary dependencies (data, libraries, code, etc.) into the package, making it lighter weight than a VMI~\cite{guo2011cde}. While both approaches provide mechanisms for sandboxing the computations associated with a scientific result, neither form of virtualization provides any guarantee that the included pieces of software will indeed reproduce the associated scientific result.

Since reproducibility includes documentation, virtualization approaches in their current form only make it easy to capture the computations. Preserving the computations so that they are easy to understand, install, or alter implicit dependencies that are part of computation is not effectively addressed, especially as dependencies and software components evolve or become deprecated. There are two approaches to address the preservation challenge. By either introducing tools that help document dependencies and provide software attribution within VMIs or packages, or alternatively by using software delivery mechanisms, such as, centralized package management, Linux containers, and the, more recent, Docker framework. We examined the first approach previously in \cite{SoftProv}. 
In this paper we examine the second approach. 
In particular, we consider the light-weight virtualization approaches, because, we believe that the combination of light-weight approaches with more standardized software delivery mechanisms can lead to addressing the reproducibility challenge for a wide variety of scientific researchers. 
A package created by those light-weight approaches encapsulates all the necessary dependencies of an application, and can be used to repeat the application through different sandbox mechanisms, including Parrot~\cite{thain2005parrot}, CDE, PTU~\cite{PTU}, chroot, and Docker~\cite{boettiger2015introduction}.

@@

To conduct a thorough examination, we consider real-world complex high energy physics (HEP) applications, independently developed by two groups, that must be reproduced so that the entire HEP community can benefit from the analysis. We describe challenges in reproducing the applications, and consider the extent to which reproducibility requirements can be satisfied with light-weight virtualization approaches and software delivery mechanisms. We propose an invariant framework for computational reproducibility that combines light-weight virtualization with software delivery mechanisms for efficiently capturing, invariantly preserving and practically deploying applications.
We measure the performance overhead of  light-weight virtualization and software delivery approaches, and show the preserved packages can be distributed to allow reproduction and verification.

### 2015-03-20 measure.tex
Remove unused stuff
Modification (according to dthain's suggestions)

We have constructed a first approximation of the invariant framework
by using and modifying a variety of existing technologies.  Of course,
a viable long-term strategy for reproducibility must not depend on a single
technology.
To this end, we have identified several technologies and techniques
that can implement each stage of the framework.

@@

Parrot~\cite{thain2005parrot} is a virtual filesystem access tool which
is used to attach applications to a variety of remote I/O systems such as HTTP, FTP, and CVMFS. It works by trapping system calls through the {\tt ptrace} interface,
replacing selected operations with remote accesses.  As a side-effect, Parrot is
also able to modify the filesystem namespace in arbitrary ways according to user
needs.  Parrot is particularly used in the high energy physics community
to provide remote access to application software.
To capture dependencies, we made small modifications to Parrot to record
the logical name of every file accessed by an application into an external
dependency list.  After execution is complete, a second tool is used to copy
all of the named dependencies into a package.

PTU~\cite{PTU,pham2014framework} is designed to create a package of an application by recording all of the binaries, libraries, scripts, data files, and environment variables used by a program.   PTU uses the CDE~\cite{guo2011cde} technology to observe system calls, but takes a snapshot of every file at the point of access.  In addition to files, PTU records \emph{metadata} about the execution environment, such as kernel versions, application versions, and dynamic library versions by using standard Unix commands.  PTU also records \emph{provenance} in the form of a graph that describes how each file is created or consumed by processes within the application.  Because PTU is focused solely on the problem of preservation, it can achieve lower overhead than Parrot when remote data access is not a requirement, as we show below.

@@

There are many possible heuristics for creating the preserved package
from the dependency list.  We have implemented three:
In a {\bf shallow copy}, we simply copy only
the exact dependencies.  Where a directory was listed, a directory is created and populated with empty files as placeholders to facilitate a directory listing.  In a {\bf medium copy},every file in every directory mentioned by the application is preserved one level deep.  In a {\bf deep copy}, every file in every directory mentioned by the application is copied recursively.  Obviously, the more aggressive the preservation, the larger the package, but the greater possibility that it can be adapted to other uses.  Other approaches to package generation might including generating the union
of multiple dependency sets, or allowing the expert user to manually add
and remove dependencies.

@@

{\bf Distribution and Deployment.}
Once generated, application packages must be collected, curated, and made
available through publically shared repositories.  There currently exist a
wide variety of services and efforts to share binary objects in this way,
and so we assume such a service will be available in the future.

@@

%\section{Measuring Dependencies}
%We have developed a prototype tool to assist in the measurement and preservation
%of implicit dependencies for complex applications.
%We use Parrot~\cite{thain2005parrot} to explicitly record all
%of the files accessed by our example application, allowing us to observe how
%much of each external dependencies is used, and what local resources are implicitly used.
%Using this information, we create a \emph{reduced package} which contains
%only the files actually used by the application.
%
%Parrot is a virtual filesystem access tool which has been used to attach
%existing programs to a variety of remote I/O systems, such as HTTP, FTP, and CVMFS.
%It works by trapping an application's system calls through the Linux {\tt ptrace} debugging
%interface, and then replacing them with the desired I/O operations.  Parrot is already used
%in the high energy physics community with applications like TauRoast specifically to 
%provide access to the CMSSW software distribution via the CVMFS distributed file system.
%We made small modifications to Parrot to record a \emph{namelist} which lists all 
%of the files that an application actually accesses.
%
%Figure~\ref{fig:workflow-parrot} illustrates the measurement process.
%The starting point of this toolkit is one successful execution of the application on the native machine.
%First, we execute the actual data analysis script under Parrot to generate the namelist.
%Then, using the namelist, we generate a package containing all the necessary data
%and software for one analysis program. When another
%researcher wants to repeat the program, he only needs to obtain the package and
%execute the actual analysis program inside the package. 
%
%For one execution of \emph{TauRoast}, the generated namelist includes 132,047 accessed filenames,
%along with the system calls used to access the file, such as {\tt open}, {\tt stat}, {\tt read}, etc.
%With duplicate filenames removed, the list is reduced to 67,168 files.
%Many of those entries do not exist, because they reflect attempts
%by the application to search for programs and libraries in multiple places.
%Only 22,068 entries reflect existing files or directories.
%
%The packaging tool iterates over each item of the filename list, determines the process
%mode and replication degree according to the file type (common files,
%directories, symbolic links) and the system call type, generates one package
%containing the dependencies, and summarizes the contents of the package
%as shown in Table~\ref{table:package-info}.  To the extent possible,
%the filesystem structure of the original environment is preserved.
%
%We considered several approaches to constructing the package.
%In a {\bf shallow copy}, we only copied the individual files in the namelist,
%creating only parent directories for each.  Where a directory was listed,
%we created the directory and populated it with empty files as placeholders
%to facilitate a directory listing.  In a {\bf medium copy}, we copied the
%individual files as before.  Where a directory was listed, we created
%the directories and copied the contents of the files in that directory,
%one level deep.  A {\bf deep copy} would duplicate all directories recursively,
%but this would have resulted in TB-sized packages, so we did not consider
%it further.
%
%Parrot is required to re-run the packaged artifact, in order to force
%the packaged files to appear to exist in their original locations.
%To this end, the packaging tool creates a \emph{file map} which maps
%the logical names of the files to their current physical locations, as shown in Table~\ref{table:map-file}.
%Parrot reads the file map and redirects system calls at run-time to achieve the desired effect.
%As the example suggests, special device files such as {\tt /proc} and {\tt /dev}
%are not incorporated into the package but are instead accessed natively.
%
%\begin{table}
%    \centering
%    \begin{tabular}{ll}
%    \hline
%    \bf Path used in Program & \bf Actual Location \\ \hline
%    {\tt /} & {\tt /tmp/package-hep} \\ \hline
%    {\tt /tmp/package-hep} & {\tt /tmp/package-hep} \\ \hline
%    {\tt /dev} & {\tt /dev} \\ \hline
%    {\tt ...} & {\tt ...}\\ \hline
%    \end{tabular}
%    \caption{Structure of Map File}
%    \label{table:map-file}
%\end{table}
%
%\begin{table}
%    \centering
%    \begin{tabular}{rrr}
%\hline
%                    & \bf Shallow Copy & \bf Medium Copy\\
%\hline
%    Whole Files    & 1632         & 15642\\ 
%\hline
%    Empty Files    & 14273        & 263\\
%\hline
%    Directories    & 1549         & 1549\\ 
%\hline
%    Symbolic Links & 4614         & 4614 \\
%\hline
%    \bf Total Size & \bf 21GB     & \bf 28GB \\ 
%\hline
%    \end{tabular}
%    \caption{Package Information}
%    \label{table:package-info}
%\end{table}

%\subsection{Tracking of Network Dependencies}
%
%\begin{figure}
%\centering
%\includegraphics[width=.6\textwidth]{git-syscall.eps}
%\caption{Exec Syscalls of a git command}
%\label{fig:git-syscall}
%\end{figure}
%
%\begin{figure}
%\centering
%\includegraphics[width=.6\textwidth]{http_packet.eps}
%\caption{HTTP Request and Response}
%\label{fig:http_packet}
%\end{figure}
%
%\begin{figure}
%\centering
%\includegraphics[width=.6\textwidth]{url_redirection.eps}
%\caption{An Example of URL Redirection}
%\label{fig:url_redirection}
%\end{figure}
%
%All the dependencies of one program can be divided into three categories: local file system (e.g., /usr, /lib and /lib64), remote file systems which can be mounted as local directories (e.g., /cvmfs and /hdfs), and other remote network dependencies (e.g. http, https and ssh).
%Through utilizing ptrace to trap each file-relevant system call used by a program, the first two categories of dependencies can be collected. 
%Motivation of tracking network dependencies: Linkrot is a common and great threat to the preservation of scientific applications. A URL which works normally today may be unavailable permanently. A method which can help the scientists figure out all the network dependencies of their applications provides the chance to evaluate the stability of each network dependencies and preserve the unstable network resources before linkrot happens.
%One direct solution to track the third category of dependencies is to utilize ptrace to check each exec system call used by a program and record each network-relevant executable and its parameters. However, an executable may create one or more child processes to finish some tasks, and a child process may create their own children processes. Figure~\ref{fig:git-syscall} shows all the processes created by a git command. A process with PID 998 is created to clone a remote git repository into local machine, which totally has 6 child processes. Moreover, a network-relevant executable name collection is necessary to identify network dependencies. The diversity of network-relevant executables and the large process tree generated for a network executable make this solution infeasible.
%
%Another solution to track network dependencies is to track the network sockets. The user process communicates with the network protocol stacks in the kernel through the network socket layer user interface on Linux. From the process tree shown in the above figure, the process with PID 1000 responds to create a socket, connect to a DNS server, send a DNS request packet to the DNS server and receive a DNS response packet from the DNS server. The information gained from the network socket tracking can be divided into three categories.
%\begin{itemize}
%\item The information of network sockets used to communicate with remote network dependences (through socket and connect system calls) can be used to figure out the port number, service name (such as, http, https, and ssh), socket type (stream and datagram),  and the domain type (inet and inet6). 
%\item The contents of DNS packets can be used to figure out the hostname and IP address of each remote network dependency. 
%\item As for applications based on http protocol, all the http requests and responses can be seen, as shown in Figure~\ref{fig:http_packet}. However, as for applications based on https and ssh which encrypt network data using TLS/SSL, tracking network data on the socket level can only see the encrypted data. 
%\end{itemize}
%
%The results of tracking network sockets used by a program involves two categories of network resource redirections, dns-level hostname redirection and website-level url redirection. 
%\begin{itemize}
%\item dns-level hostname redirection: Each DNS packet includes five parts, header, question, answer, authority, and additional. A DNS response packet with the type CNAME has multiple answers. For example, the DNS response packet which tries to resolve {\tt www3.nd.edu} includes two answers. The first answer provides an alias of {\tt www3.nd.edu}, {\tt www-vip.cc.nd.edu}, and the second answer maps the alias to the IP address. 
%{\tt www3.nd.edu} CNAME {\tt www-vip.cc.nd.edu}
%{\tt www-vip.cc.nd.edu} A {\tt 129.74.12.151}
%The CNAME-type DNS packets leave us a question, among the hostname used by the user, the alias(es), the IP address, what should we preserve?
%\item website-level url redirection: Website-level url redirection happens when a website updates its location and still want their old users access their resources using the old url. Figure~\ref{fig:url_redirection} illustrates the url redirection between {\tt \url{www3.nd.edu/~ccl}} and {\tt ccl.cse.nd.edu}. Except for the difference of hostnames, the application layer protocols used by the old-version website and the new-version website is also different: the old website provides services through the https protocol, while the new website provides services through the http protocol. 
%\end{itemize}
%
%The usage of https protocol makes detecting of website-level url redirections through tracking system calls more difficulty and even impossible. All the application data will be encrypted at presentation layer through the TLS/SSL protocol, which is initialized at the session layer and works at the presentation layer.

>>>>

We have constructed a first approximation of the invariant framework
by using and modifying a variety of existing technologies.  Of course,
a viable long-term strategy for reproducibility must not depend on a single
technology.
To this end, we have identified multiple technologies 
that can implement each stage of the framework.

@@

Parrot is a virtual filesystem access tool which
is used to attach applications to a variety of remote I/O systems such as HTTP, FTP, and CVMFS. It works by trapping system calls through the {\tt ptrace} interface,
replacing selected operations with remote accesses.  As a side-effect, Parrot is
also able to modify the filesystem namespace in arbitrary ways according to user
needs.  Parrot is particularly used in the high energy physics community
to provide remote access to application software via CVMFS.
To capture dependencies, we made small modifications to Parrot to record
the logical name of every file accessed by an application into an external
dependency list.  After execution is complete, a second tool is used to copy
all of the named dependencies into a package.

PTU~\cite{pham2014framework} is designed to create a package of an application by recording all of the binaries, libraries, scripts, data files, and environment variables used by a program.   PTU uses the CDE technology to observe system calls, but takes a snapshot of every file at the point of access.  In addition to files, PTU records \emph{metadata} about the execution environment, such as kernel versions, application versions, and dynamic library versions by using standard Unix commands.  PTU also records \emph{provenance} in the form of a graph that describes how each file is created or consumed by processes within the application.  Because PTU is focused solely on the problem of preservation, it can achieve lower overhead than Parrot when remote data access is not a requirement, as we show below.

@@

There are many possible heuristics for creating the preserved package
from the dependency list.  We have implemented three:
In a {\bf shallow copy}, we copy only
the exact dependencies.  Where a directory was listed, a directory is created and populated with empty files as placeholders to facilitate a directory listing.  In a {\bf medium copy},every file in every directory mentioned by the application is preserved one level deep.  In a {\bf deep copy}, every file in every directory mentioned by the application is copied recursively.  Obviously, the more aggressive the preservation, the larger the package, but the greater possibility that it can be adapted to other uses.  Other approaches to package generation might including generating the union
of multiple dependency sets, or allowing the expert user to manually add
and remove dependencies.

@@

{\bf Distribution and Deployment.}
Once generated, application packages must be collected, curated, and made
available through publically shared repositories.  There currently exist a
wide variety of services and efforts to share binary objects in this way,
and so we assume such multiple services will be available in the future.

@@

### 2015-03-20 observation.tex
Modification (according to dthain's suggestions)

\section{Challenges and Observations in Reproducing HEP Applications}

The \emph{TauRoast} and \emph{Athena} application specification was provided to us in the form of an
email which described, in prose, how to obtain the source,
build the program, and run it correctly on one specific
machine at our home institution, with no particular guarantee that
it will run anywhere else in the world. Such level of documentation and exchange of information about a software is typically routine in the scientific world. 
We provide the challenges we faced in capturing the application details in a reproducible form and then preserving it for subsequent reuse:

@@

\item {\bf Identifying all dependencies.}  Due to the distributed nature of HEP applications, the applications typically depend on a large number of external and local dependencies.
External dependencies are often explicitly stated, such as when the application makes connections to Github resources, and CVS servers for downloading source. 
However, when the application has distributed execution then implicit network connections are present requiring us to identify dependencies on all machines where execution takes place. 
Implicit local dependencies arise due to mounted filesystems. In \emph{TauRoast}, the application data and code is distributed on five networked filesystems, and in \emph{Athena} on two networked filesystems. 
Since these filesystems appear local to the application machine, it is important to check and capture mounted filesystems and their respective mount points.

\item {\bf Configuration Complexity.} To correctly reproduce an application implies that run-time configurations and consistency checks on the available software are effectively captured and preserved. 
For CMS,  {\tt scram} software management tool, is used to locate
the appropriate version of software,  set environment variables such as the PATH, run any
tool-specific configuration, and do the same for all software on which it depends. A reproducible framework must capture the work of such software management tools so that they can conduct similar
checks on a new machine.

@@

\item {\bf Rapid Changes in Dependencies.}  Over the course of three months
between collecting the initial email, analyzing the program, and writing this
paper, the computing environment continuously changed.  The CMSSW software
distribution released a new version, the target execution environment was upgraded
to a new operating system, and the application deprecated the use of CVS for obtaining
the software. In Athena, the computing environment can potentially change daily, since upgrades to the software framework occur on a nightly basis.  
While the users of this software seem be accustomed to constant change,
any preservation technique will have to be very cautious about relying upon an
external service, even one that may appear to be highly stable.

>>>>

\section{Challenges in Reproducing HEP Applications}

The \emph{TauRoast} and \emph{Athena} application specification was provided to us in the form of an
email which described, in prose, how to obtain the source,
build the program, and run it correctly on one specific
machine at our home institution, with no particular guarantee that
it will run anywhere else in the world. This minimal level of documentation about software is routine in the scientific world. 
We provide the challenges we faced in capturing the application details in a reproducible form and then preserving it for subsequent reuse:

@@

\item {\bf Identifying all dependencies.}  Due to the distributed nature of HEP applications, these applications depend on a large number of external and local dependencies.
External dependencies are often explicitly stated, such as when the application makes connections to Github resources, and CVS servers for downloading source. 
However, when the application has distributed execution then implicit network connections are present requiring us to identify dependencies on all machines where execution takes place. 
Implicit local dependencies arise due to mounted filesystems. In \emph{TauRoast}, the application data and code is distributed on five networked filesystems, and in \emph{Athena} on two networked filesystems. 
Since these filesystems appear local to the application machine, it is important to check and capture mounted filesystems and their respective mount points.

\item {\bf Configuration Complexity.} To correctly reproduce an application implies that run-time configurations and consistency checks on the available software are effectively captured and preserved. 
For CMS,  the {\tt scram} software management tool is used to locate
the appropriate version of software,  set environment variables such as the PATH, run any
tool-specific configuration, and do the same for all software on which it depends. A reproducible framework must capture the work of such software management tools so that they can conduct similar
checks on a new machine.

@@

\item {\bf Rapid Changes in Dependencies.}  Over the course of three months
between collecting the initial email, analyzing the program, and writing this
paper, the computing environment continuously changed.  The CMSSW software
distribution released a new version, the target execution environment was upgraded
to a new operating system, and the application switched from CVS to Git for obtaining
the software. In Athena, the computing environment can potentially change daily, since upgrades to the software framework occur on a nightly basis.  
While the users of this software seem be accustomed to constant change,
any preservation technique will have to be very cautious about relying upon an
external service, even one that may appear to be highly stable.

### 2015-03-20 tauroast.tex
Modification (according to dthain's suggestions)

We study applications taken from two experiments of the CERN Large Hadron Collider, namely the ATLAS experiment and the CMS experiment. 
One of the applications of the ATLAS experiment is the \emph{Athena} application, which is a general purpose processing framework including algorithms
for event reconstruction and data reduction \cite{calafiura2005athena}. The CMS experiment is conducted through an application termed  \emph{TauRoast}, which searches for specific 
cases where the Higgs boson decays to two tau leptons~\cite{chatrchyan2013search}. In LHC, the ATLAS and CMS experiments are distinct, 
developed independently by two entirely separate physics communities. Consequently, their applications  
have very different software distribution and data management frameworks, making it interesting to examine if common reproducibility frameworks and 
tools work across the two communities.

Code and data in \emph{TauRoast} is available through five different networked filesystems, namely an HDFS cluster for data files, 
some configuration files were stored on a CVMFS~\cite{blomer2011cernvm} filesystem, and a variety of software tools were on an NFS, PanFS and AFS systems.
In addition, code may exist in version control systems such as Git, CVS, and CMS Software Distribution (CMSSW). %~\cite{cms2006cms}. 
\begin{wrapfigure}{r}{0.4\textwidth}
\small
\centering
\includegraphics[width=.4\textwidth]{data-code-size.eps}
\caption{Inputs to Tau Roast}
\label{fig:data-code-size}
\end{wrapfigure}
Data that is input to \emph{TauRoast} is obtained by reducing it through a pipeline, as shown in Figure \ref{fig:data-code-size}. Consequently, the real input data may 
vary depending upon the science question being researched. Similarly the software may name many possible components but the used components are
smaller than the named ones.

>>>>

We study applications taken from two experiments of the CERN Large Hadron Collider, namely the ATLAS experiment and the CMS experiment. 
In LHC, the ATLAS and CMS experiments are distinct, 
developed independently by two entirely separate physics communities. Consequently, their applications  
have very different software distribution and data management frameworks, making it interesting to examine if common reproducibility frameworks and 
tools work across the two communities. 
One of the applications of the ATLAS experiment is the \emph{Athena} application, which is a general purpose processing framework including algorithms
for event reconstruction and data reduction \cite{calafiura2005athena}. The CMS experiment is conducted through an application termed  \emph{TauRoast}, which searches for specific 
cases where the Higgs boson decays to two tau leptons~\cite{chatrchyan2013search}.

Code and data in \emph{TauRoast} is available through five different networked filesystems which are mounted locally, an HDFS cluster for data, 
some configuration files were stored on CVMFS~\cite{blomer2011cernvm}, and a variety of software tools were on an NFS, PanFS and AFS systems.
In addition, code may exist in version control systems such as Git, CVS, and CMS Software Distribution (CMSSW). %~\cite{cms2006cms}. 
\begin{wrapfigure}{r}{0.4\textwidth}
\small
\centering
\includegraphics[width=.4\textwidth]{data-code-size.eps}
\caption{Inputs to Tau Roast}
\label{fig:data-code-size}
\end{wrapfigure}
Data that is input to \emph{TauRoast} is obtained by reducing it through a pipeline, as shown in Figure \ref{fig:data-code-size}. Consequently, the real input data may 
vary depending upon the science question being researched. Similarly the software may name many possible components but the used components are
smaller than the named ones.
